The 18.821 Mathematics Project Lab Report [Proofs]

### 2013-09-28 paper.tex
Changing the definitions.

\begin{definition}
  A path $\gamma: \mathrm{R} \to \mathrm{R}^2$ is a function which maps some time $t$ to a position $\gamma(t) \in \mathrm{R}^2$. The path is defined from time $t = 0$ until the end time of the path, denoted as $T_{f}(\gamma)$.
\end{definition}

\begin{definition}
  A valid path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some point mass $p$ and conditions $\mathrm{C}$ is some path which at all times $t$ such that $0 \leq t \leq T_f(\gamma)$, all conditions in $\mathrm{C}$ are satisfied.
\end{definition}

>>>>

\begin{definition}
  A description of a particle $p$ is a set $D(t)$ which contains a particle's position $\vec{x} \in \mathrm{R}^2$ and its derivatives at some time $t$. In other words, we define $D(t) = \{ \vec{x}(t), \frac{d \vec{x}}{dt}(t), \frac{d^2 \vec{x}}{d t^2}(t), \ldots \}$.
\end{definition}

\begin{definition}
  A condition $c$ on a particle $p$ is a boolean function $c: \mathrm{D} \to \{0,1\}$ which takes as input a description $D(t)$ of the particle $p$ at some time $t$ and outputs that either the condition is true or false.
\end{definition}

\begin{definition}
A path $\gamma: \mathrm{R} \to \mathrm{R}^2$ is a function which maps some time $t$ to a position $\gamma(t) \in \mathrm{R}^2$. The path is defined from time $t = 0$ until the end time of the path, denoted as $T_{f, \gamma}$.
\end{definition}

\begin{definition}
  A valid path $\gamma: \mathrm{R} \to \mathrm{R}^2$ for some particle $p$ and conditions $\mathrm{C}$ is some path which at all times $t$ such that $0 \leq t \leq T_{f, \gamma}$, all conditions in $\mathrm{C}$ on the particle are satisfied.
\end{definition}
